Outbreak Threshold Detection

### 2023-03-06 notebooks/Julia/simulation-detection.qmd
Update simulation functions to account for E and N compartments and update to median Update calculation of average to use median to specify dims, as is likely quicker than my loop implementation

```{julia}
function run_sir_sim(; u₀, tspan, p)
    prob = DiscreteProblem(u₀, tspan, p)
    jump_prob = JumpProblem(prob, Direct(), rj)
    sol_jump = solve(jump_prob, TauLeaping(); dt = δt)
    return sol_jump(0:δt:tmax);
end
```

```{julia}
function create_sim_array(; out_jump)
    test_array[1:3, :] = Array(out_jump)
    test_array[4, :] .= out_jump.t

    return test_array
end
```

@@

sir_array = zeros(Float64, 4, tlength)
all_sims_array = zeros(Float64, 4, tlength, nsims)
sim_means = zeros(Float64, 3, tlength)

@showprogress for i in 1:nsims
    out_jump = run_sir_sim(u₀ = u₀, tspan = tspan, p = p)
    sir_array = create_sim_array(out_jump = out_jump)

@@

    lines!(ax, sir_array[4, :], sir_array[1, :], linewidth = 4, color = ("dodgerblue4", 0.01))
    lines!(ax, sir_array[4, :], sir_array[2, :], linewidth = 4, color = ("firebrick3", 0.01))
    lines!(ax, sir_array[4, :], sir_array[3, :], linewidth = 4, color = ("chocolate2", 0.01))

@@

@showprogress for sim in 1:tlength, outcome in 1:3
    sim_means[outcome, sim] = mean(all_sims_array[outcome, sim, :])
end

lines!(ax, sir_array[4, :], sim_means[1, :], linewidth = 3, color = "dodgerblue4")
lines!(ax, sir_array[4, :], sim_means[2, :], linewidth = 3, color = "firebrick3")
lines!(ax, sir_array[4, :], sim_means[3, :], linewidth = 3, color = "chocolate2")

>>>>

```{julia}
function run_sir_sim(; u₀, tspan, p)
    prob = DiscreteProblem(u₀, tspan, p)
    jump_prob = JumpProblem(prob, Direct(), gillespie_jumps..., save_positions = (false, false))
    jump_sol = solve(jump_prob, SSAStepper(), saveat = δt)
    return jump_sol;
end
```

```{julia}
out_jump = run_sir_sim(u₀ = u₀, tspan = tspan, p = p)
Array(out_jump)
```

```{julia}
function create_sim_array!(; out_jump)
    sir_array[1:4, :] = Array(out_jump)
    sir_array[5, :] = sum(sir_array[1:4, :], dims = 1) 
    sir_array[6, :] .= out_jump.t

    return nothing
end
```

@@

sir_array = zeros(6, tlength + 1)

all_sims_array = zeros(Float64, 6, tlength + 1, nsims)
sim_means = zeros(Float64, 5, tlength + 1)

@showprogress for i in 1:nsims
    out_jump = run_sir_sim(u₀ = u₀, tspan = tspan, p = p)
    create_sim_array!(out_jump = out_jump)

@@

    lines!(ax, sir_array[6, :], sir_array[1, :], linewidth = 4, color = ("dodgerblue4", 0.02))
    lines!(ax, sir_array[6, :], sir_array[2, :], linewidth = 4, color = ("firebrick3", 0.02))
    lines!(ax, sir_array[6, :], sir_array[3, :], linewidth = 4, color = ("chocolate2", 0.02)) 
    lines!(ax, sir_array[6, :], sir_array[4, :], linewidth = 4, color = ("green", 0.02)) 
    lines!(ax, sir_array[6, :], sir_array[5, :], linewidth = 4, color = ("purple", 0.02))

@@

@showprogress for outcome in 1:5
    sim_means[outcome, :] = median(all_sims_array[outcome, :, :], dims = 2)
end

lines!(ax, sir_array[6, :], sim_means[1, :], linewidth = 3, color = "dodgerblue4", label = "S(t)")
lines!(ax, sir_array[6, :], sim_means[2, :], linewidth = 3, color = "firebrick3", label = "E(t)")
lines!(ax, sir_array[6, :], sim_means[3, :], linewidth = 3, color = "chocolate2", label = "I(t)")
lines!(ax, sir_array[6, :], sim_means[4, :], linewidth = 3, color = "green", label = "R(t)")
lines!(ax, sir_array[6, :], sim_means[5, :], linewidth = 3, color = "purple", label = "N(t)")
